Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2017-02-14 inst/examples/20170201-manuscript.Rmd
updateing analyses

for (catal in unique(df$catalog)) {
  dfs <- subset(df, catalog == catal)
  p <- ggplot(dfs, aes(x = publication_decade, y = mean_title_length)) +
       geom_point(aes(size = n), size = 5) +
       geom_line(size = 1) +
       ylab("Title length (word count)") +
       xlab("Publication decade") +
       ggtitle(paste("Mean title length (", catal, ")", sep = ""))

  print(p)
}
```

@@

### Fig 6: Publishing activity over time

@@

# Add indicator of the publication period
df$period <- cut(df$publication_year,
           breaks = c(1757, 1766, 1775, 1783),
		 include.lowest = TRUE,
		 right = FALSE
		 )
df$period <- gsub("\\[", "", df$period)
df$period <- gsub("\\)", "", df$period)
df$period <- gsub(",", ",", df$period)

@@

  p <- p + geom_text(data = rectangles, angle = 90, aes(x=xmin + .5, y=.9*ymax, label=place), size = 6)

@@

p <- ggplot(df, aes(x = publication_year, y = n)) +
     geom_bar(stat = "identity") +
     ggtitle("") +
     scale_x_continuous(breaks = seq(minyear, maxyear, 5)) +
     xlab("Publication year") +
     ylab("Title count")

>>>>

  p <- ggplot(df, aes(x = publication_decade, y = mean_title_length, fill = catalog)) +
       geom_bar(stat = "identity", color = "black", position = "dodge") +
       #geom_point(aes(size = n), size = 5) +
       #geom_line(size = 1) +
       scale_fill_manual(values = c("darkgray", "black")) +
       guides(fill = guide_legend(title = "Place", reverse = TRUE)) +       
       ylab("Title length (word count)") +
       xlab("Publication decade") +
       ggtitle(paste("Mean title length (", catal, ")", sep = ""))

  print(p)

@@

### Fig 6: Publishing activity over time (Kungliga)

@@

# Add indicator of the publication period
df$period <- cut(df$publication_year,
           breaks = c(1757, 1766, 1775, 1783),
		 include.lowest = TRUE,
		 right = FALSE
		 )
df$period <- gsub("\\[", "", df$period)
df$period <- gsub("\\)", "", df$period)
df$period <- gsub(",", ",", df$period)
df$period <- gsub("\\]", ",", df$period)

@@

@@

p <- ggplot(df, aes(x = publication_year, y = n)) +
     geom_bar(stat = "identity") +
     ggtitle("") +
     scale_x_continuous(breaks = seq(minyear, maxyear, 5)) +
     xlab("Publication year") +
     ylab("Title count (n)")
